Notes for ISIPTA poster

### 2016-07-15 asce-paper.tex
start sec 4.1

Observing a one of a kind system with $n_k$ components of type $k$ running until $\tnow$,
where $e_k$ components have failed by $\tnow$, and $n_k - e_k$ components still function:
\begin{linenomath*}
\begin{align}
\mbf{t}^k_{e_k;n_k} &= \big( \underbrace{t^k_1, \ldots, t^k_{e_k}}_{e_k \text{failure times}},
                             \underbrace{\tpnow, \ldots, \tpnow}_{n_k-e_k \text{censored obs.}} \big)
\end{align}
\end{linenomath*}

>>>>

Consider observing a prototype system until $\tnow$,
where the system has $K$ different types of components,
and for each type $k$ there are $n_k$ components in the system.
Denoting the number of type $k$ components that have failed by $\tnow$ by $e_k$,
there are $n_k - e_k$ components still functioning at $\tnow$.
We denote the corresponding vector of observations by
\begin{linenomath*}
\begin{align}
\mbf{t}^k_{e_k;n_k} &= \big( \underbrace{t^k_1, \ldots, t^k_{e_k}}_{e_k \text{failure times}},
                             \underbrace{\tpnow, \ldots, \tpnow}_{n_k-e_k \text{censored obs.}} \big)\,,
\end{align}
\end{linenomath*}
where $t^+$ indicates a censored observation.
